---
title: "Data Analysis for the Composite Face Task (104_6)"
author: "[Haiyang Jin](https://haiyangjin.github.io/)"
date:  "`r format(Sys.time(), '%d-%m-%Y')`"
knit: ""
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 4
    toc_float: true
    includes:
        after_body: Utilities/footer.html
output_dir: output/
params:
    output_dir: output/
version: "4.0"
---

```{r setup, include=FALSE}
## set chunk options
knitr::opts_chunk$set(echo = TRUE)
```

# Preparation
```{r load the related libraries, message=FALSE}
## load libraries
library(tidyverse)
library(ez)
library(lme4)
library(lmerTest)


# set up the theme for plot and rainclound plot
plot_theme = theme(
  text = element_text(size = 10),
  axis.title = element_text(size = 16), 
  axis.text = element_text(size = 14), # the size of the texts in plot
  # axis.text.x = element_text(angle = 45, vjust = 0.5),
  legend.title=element_text(size=16),
  legend.text=element_text(size=16),
  legend.position = "right",
  legend.key.width = unit(1.2, "cm"),
  plot.title = element_text(lineheight=.8, face="bold", size = 17),
  panel.border = element_blank(),
  panel.grid.minor = element_blank(),
  panel.grid.major = element_blank(),
  axis.line.x = element_line(colour = 'black', size=0.5, linetype='solid'),
  axis.line.y = element_line(colour = 'black', size=0.5, linetype='solid', arrow = arrow(length = unit(0.3, "cm"))),
  # remove the facet background color
  strip.text = element_text(face="bold", size=12, lineheight=5.0),
  strip.background = element_rect(fill="white", colour="white", size=1),
  strip.placement = "outside"
)

source(file.path("R", "geom_flat_violin.R"))
    
```

This R markdown file analyzed the data for the <b>composite face task (complete design)</b> without <b>catch trials</b>. (Experiment number is 104_6) 

```{r input all the information about the data set}
###### Optional ######
## the filename of the raw data file 
fn.raw <- file.path("data","104_106_n-20_2017-05-04-1446.csv")

## input the filename of the output file (.csv)
output.name <- "E1_104_106"

```

```{r save CSV, include = FALSE}
# do you want save the data into *.csv files
# saveCSV = TRUE
saveCSV = FALSE
path.output <- file.path("output", ".")

# set the filenames for R and SPSS data format
output.d.R <- file.path(path.output, paste0(output.name, "_d_R.csv"))
output.d.SPSS <- file.path(path.output, paste0(output.name, "_d_SPSS.csv"))
output.rt.R <- file.path(path.output, paste0(output.name, "_rt_R.csv"))
output.rt.SPSS <- file.path(path.output, paste0(output.name, "_rt_SPSS.csv"))

```

The raw data was loaded from the file named `r basename(fn.raw)` in the `r dirname(fn.raw)`/ folder. 

# Tidying up the data
```{r read the raw data file and set the name for output file, message = FALSE}
# read data file
df.raw <- read_csv(fn.raw)
str(df.raw)
```


```{r calculate the Z value for RT and clean data}
# clean and rename the levels of independent variables
df.clean <- {
  df.raw %>%
    tbl_df() %>%  # change into table data frame format
    mutate(
      Participant = as.factor(Participant),
      Congruency = as.factor(Congruency),
      Alignment = as.factor(Alignment),
      Experiment = as.factor(Experiment),
      Congruency = recode(Congruency, "C" = "congruent", "I" = "incongruent"), # rename the levels for Congruency
      Alignment = recode(Alignment, "A" = "aligned", "M" = "misaligned"),
      Experiment = recode(Experiment, "104_CF_CFS" = "CFS", "106_CF_Mono" = "monocular")
      ) %>% # rename the levels for Alignment
    group_by(Experiment, Participant, Congruency, Alignment, SameDifferent, isCorrect) %>% # divide into groups 
    mutate(
      RT.Z = scale(reactionTime), # calculate the Z value for response times within each group
      RT.Within3Z = ifelse(RT.Z <= 3 & RT.Z >= -3, 1, ifelse(RT.Z < -3 | RT.Z > 3, 0, NaN))
      ) %>%  # if the Z values are between -3 and 3, will be marked as 1. 
      mutate(Stimuli = paste(StudyUpper, StudyLower, TargetUpper, TargetLower, sep = "-")) %>%
    ungroup()  # ungroup the data
}

df.clean

```


# Sensitivity d'
```{r calculate the sensitivity d for R analysis}
# calculate the d'
individual.d.R <- { # get the hit and correct rejection rates
  df.clean %>%
    group_by(Experiment, Participant, Congruency, Alignment, SameDifferent) %>%  # divide the data into serveral groups 
    summarize(Accuracy = mean(isCorrect), Count = n()) %>% # get accuracy and count for each condition (hit and correct rejection)  
    mutate(Accuracy = ifelse(Accuracy == 1, 1 - 0.5/Count, Accuracy)) %>%  # set 1 equals to 1-0.5/n
    spread(SameDifferent, Accuracy) %>%  # spread the Accuracy into two columns based on SameDifferent
    mutate(FA = 1 - D,
           Z.hit = qnorm(S),
           Z.FA = qnorm(FA),
           dprime = Z.hit - Z.FA) %>% # get the d prime
    select(Experiment, Participant, Congruency, Alignment, dprime, Count)
}

# descriptive statistics of d for plotting
sum.d.R <- {
  individual.d.R %>% 
    group_by(Experiment, Congruency, Alignment) %>% 
    summarize(Mean = mean(dprime), N = n(), SD = sd(dprime), SE = SD/sqrt(N), SE.hi = Mean + SE, SE.lo = Mean - SE, CI = SE * qt(0.975,N), Median = median(dprime), Lower = Mean - SD, Upper = Mean + SD) %>% 
    ungroup()
}

# d for SPSS sytle analysis
individual.d.SPSS <- {
  individual.d.R %>%
    ungroup() %>%  # ungroup the data.d.r 
    mutate(Conditions = paste(Experiment, Congruency, Alignment, sep = ".")) %>% # combine all the levels together
    select(Participant, dprime, Conditions, Count) %>% # delete the Independet Variables
    spread(Conditions, dprime)
}

# save the d' for R analysis
if (saveCSV) {
  write.csv(individual.d.R, output.d.R, row.names = FALSE)
  write.csv(individual.d.SPSS, output.d.SPSS, row.names = FALSE)
}

```


## RainClound plot of sensitivity (d')
```{r rainclound plot of sensitivity}
knitr::kable(sum.d.R, digits = 4)

d.RainPlot <- {
  ggplot(data = individual.d.R, aes(y = dprime, x = Alignment, fill = Congruency)) + 
    geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .7) +
    geom_point(aes(y = dprime, color = Congruency), position = position_jitter(width = .15), size = .5, alpha = .8) +
    geom_boxplot(aes(y = dprime), width = .2, outlier.shape = NA, alpha = .7) +
    geom_point(data = sum.d.R, aes(y = Mean, x = Alignment, color = Congruency), position = position_nudge(x = 0.3), size = 2.5) +
    geom_errorbar(data = sum.d.R, aes(y = Mean, ymin = Lower, ymax = Upper), position = position_nudge(x = 0.3), width = 0) +
    facet_grid(. ~ Experiment, switch = "both") +
    # scale_colour_grey() + # start = .1, end = .6, color for the contour
    # scale_fill_grey() + # start = .3, end = .6, color for the fill
    # scale_color_brewer(palette = "Set1") +
    # scale_fill_brewer(palette = "Set1") +
    labs(title = "Sensitivity d' for E104_106", x = "Experiment", y = "Sensitivity", fill = "Congruency", color = "Congruency") +  # set the names for main, x and y axises and the legend
    # coord_cartesian(ylim = c(0, 6)) +  # set the limit for y axis
    # scale_y_continuous(expand= c(0, 0)) +  # remove the space between columns and x axis
    # geom_hline(yintercept = 0, linetype = 5, alpha = 0.5) + # add the line for 0.5 and 1 (y)
    theme_bw() + # the backgroud color
    plot_theme
}

```

&nbsp;

```{r display the RainCloud plot for sensitivity (d)}
d.RainPlot
```


## Repeated measure ANOVA for sensitivity (d')
### Sensitivity d': Experiment(2) $\times$ Congruency(2) $\times$ Alignment(2)
```{r repeated measure ANOVA for d}

d.anova <- { 
  ezANOVA(data = individual.d.R
          , dv = dprime
          , wid = Participant
          , within = c(Experiment, Congruency, Alignment)
          , detailed = TRUE
          # , type = 3 # for this test, results for type II and III are the same
          # , return_aov = TRUE
  )
}

knitr::kable(d.anova$ANOVA, digits = 4)
```


```{r include = FALSE}
thisExp <- unique(df.clean$Experiment)[1]
```

### Sensitivity d' for `r thisExp`: Congruency(2) $\times$ Alignment(2)
```{r ANOVA of sensitivity d for CF with CFS}
d.anova.CFS <- {
  individual.d.R %>%
    filter(Experiment == thisExp) %>% 
    ezANOVA(
      dv = dprime,
      wid = Participant,
      within = .(Congruency, Alignment),
      detailed = TRUE,
      return_aov = TRUE
    )  # run repeaed measures ANOVA 
}

knitr::kable(d.anova.CFS$ANOVA, digits = 4)

```


```{r include = FALSE}
thisExp <- unique(df.clean$Experiment)[2]
```

### Sensitivity d' for `r thisExp`: Congruency(2) $\times$ Alignment(2)
```{r ANOVA of sensitivity d for CF with monocular}
d.anova.CFS <- {
  individual.d.R %>%
    filter(Experiment == thisExp) %>% 
    ezANOVA(
      dv = dprime,
      wid = Participant,
      within = .(Congruency, Alignment),
      detailed = TRUE,
      return_aov = TRUE
    )  # run repeaed measures ANOVA 
}

knitr::kable(d.anova.CFS$ANOVA, digits = 4)
```


## Line plot of sensitivity (d')
```{r Plot of d}

d.ColuPlot = {
  ggplot(data = sum.d.R, aes(y = Mean, x = Alignment, color = Congruency, group = Congruency)) +  # set the data, varialbes for x and y axises, and the variable for dividing data
    geom_point() +
    geom_line() +  # position = "dodge", alpha = .7
    geom_errorbar(mapping = aes(ymin = SE.lo, ymax = SE.hi), linetype = 1,  # set the error bar
                  show.legend = FALSE, width = 0.25, alpha = .5) + # ,                   position = position_dodge(width=0.9)
    facet_grid(. ~ Experiment, switch = "both") +
    coord_cartesian(ylim = c(0, 4.5)) +  # set the limit for y axis
    scale_y_continuous(expand= c(0, 0)) +  # remove the space between columns and x axis
    labs(title = "Sensitivity for E104_106", x = "Experiment", y = "Sensitivity", fill = "Congruency") +  # set the names for main, x and y axises
    scale_fill_grey() +  # set the color for columns
    geom_text(label = c("", "", "", "", "***", "", "", ""), color = "red", size = 6, nudge_y = 0.5, nudge_x = 0.5) + # add starts to the significant columns
    theme_bw() +
    plot_theme
}

d.ColuPlot
```



# Correct Response Times
```{r calculate the correct response times for R analysis}
individual.rt.R <- {
  df.clean %>%
    filter(RT.Within3Z == 1)  %>%  # only keep the RT within 3 Z
    filter(isCorrect == 1)  %>%  # only keep the correct correct
    group_by(Experiment, Participant, Congruency, Alignment) %>%  # divide the data into serveral groups 
    summarize(RT = mean(reactionTime) * 1000 + 300, Count = n()) %>% # get RT and count for each condition
    ungroup()
}

# descriptive statistics of RT for plotting
sum.rt.R <- {
  individual.rt.R %>% 
    select(-Count) %>% 
    group_by(Experiment, Congruency, Alignment) %>% 
    summarize(Mean = mean(RT), N = n(), SD = sd(RT), SE = SD/sqrt(N), SE.hi = Mean + SE, SE.lo = Mean - SE, CI = SE * qt(0.975,N), Median = median(RT), Lower = Mean - SD, Upper = Mean + SD) %>% 
    ungroup()
}

# RT for SPSS sytle analysis
individual.rt.SPSS <- {
  individual.rt.R %>%
    mutate(Conditions = paste(Experiment, Congruency, Alignment, sep = ".")) %>%
    select(Participant, Conditions, RT) %>% 
    spread(Conditions, RT)
}

# save the RT for R analysis
if (saveCSV) {
  write.csv(individual.rt.R, output.rt.R, row.names = FALSE)
  write.csv(individual.rt.SPSS, output.rt.SPSS, row.names = FALSE)
}

```


## RainClound plot of correct response times
```{r rainclound plot of correct response times}
knitr::kable(sum.rt.R, digits = 4)

rt.RainPlot <- {
  ggplot(data = individual.rt.R, aes(y = RT, x = Alignment, fill = Congruency)) + 
    geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .7) +
    geom_point(aes(y = RT, color = Congruency), position = position_jitter(width = .15), size = .5, alpha = .8) +
    geom_boxplot(aes(y = RT), width = .2, outlier.shape = NA, alpha = .7) +
    geom_point(data = sum.rt.R, aes(y = Mean, x = Alignment, color = Congruency), position = position_nudge(x = 0.3), size = 2.5) +
    geom_errorbar(data = sum.rt.R, aes(y = Mean, ymin = Lower, ymax = Upper), position = position_nudge(x = 0.3), width = 0) +
    facet_grid(. ~ Experiment, switch = "both") +
    # scale_colour_grey() + # start = .1, end = .6, color for the contour
    # scale_fill_grey() + # start = .3, end = .6, color for the fill
    # scale_color_brewer(palette = "Set1") +
    # scale_fill_brewer(palette = "Set1") +
    labs(title = "Correct Response Times for E104_106", x = "Alignment", y = "Response Times (ms)", fill = "Congruency", color = "Congruency") +  # set the names for main, x and y axises and the legend
    # coord_cartesian(ylim = c(0, 6)) +  # set the limit for y axis
    # scale_y_continuous(expand = c(0, 0)) +  # remove the space between columns and x axis
    # geom_hline(yintercept = 0, linetype = 5, alpha = 0.5) + # add the line for 0.5 and 1 (y)
    theme_bw() + # the backgroud color
    plot_theme
}

```


&nbsp;

```{r display the RainCloud plot for response times}
rt.RainPlot
```


## Repeated measure ANOVA for response times
### Correct RT: Experiment(2) $\times$ Congruency(2) $\times$ Alignment(2)
```{r repeated measure ANOVA for response times}

rt.anova <- { 
  ezANOVA(data = individual.rt.R
          , dv = RT
          , wid = Participant
          , within = c(Experiment, Congruency, Alignment)
          , detailed = TRUE
          # , type = 3 # for this test, results for type II and III are the same
          # , return_aov = TRUE
  )
}

knitr::kable(rt.anova$ANOVA, digits = 4)
```



```{r include = FALSE}
thisExp <- unique(df.clean$Experiment)[1]
```

### Correct RT for `r thisExp`: Congruency(2) $\times$ Alignment(2)
```{r ANOVA of Correct RT for CF with CFS}
rt.anova.CFS <- {
  individual.rt.R %>%
    filter(Experiment == thisExp) %>%
    ezANOVA(
      dv = RT,
      wid = Participant,
      within = .(Congruency, Alignment),
      detailed = TRUE,
      return_aov = TRUE
    )  # run repeaed measures ANOVA 
}

knitr::kable(rt.anova.CFS$ANOVA, digits = 4)
```


```{r include = FALSE}
thisExp = unique(df.clean$Experiment)[2]
```

### Correct RT for `r thisExp`: Congruency(2) $\times$ Alignment(2)
```{r ANOVA of Correct RT for CF with monocular}
rt.anova.CFS <- {
  individual.rt.R %>%
    filter(Experiment == thisExp) %>%
    ezANOVA(
      dv = RT,
      wid = Participant,
      within = .(Congruency, Alignment),
      detailed = TRUE,
      return_aov = TRUE
    )  # run repeaed measures ANOVA 
}

knitr::kable(rt.anova.CFS$ANOVA, digits = 4)
```


## Line plot of correct response times
```{r Plot of correct response times}

rt.ColuPlot = {
  ggplot(data = sum.rt.R, aes(y = Mean, x = Alignment, color = Congruency, group = Congruency)) +  # set the data, varialbes for x and y axises, and the variable for dividing data
    geom_point() +
    geom_line() +  # position = "dodge", alpha = .7
    geom_errorbar(mapping = aes(ymin = SE.lo, ymax = SE.hi), linetype = 1,  # set the error bar
                  show.legend = FALSE, width = 0.25, alpha = .5) + # ,                   position = position_dodge(width=0.9)
    coord_cartesian(ylim = c(0, 1100)) +  # set the limit for y axis
    scale_y_continuous(expand= c(0, 0)) +  # remove the space between columns and x axis
    facet_grid(. ~ Experiment, switch = "both") +
    labs(title = "Correct Response Times for E104_106", x = "Experiment", y = "Response Times (ms)", fill = "Congruency") +  # set the names for main, x and y axises
    scale_fill_grey() +  # set the color for columns
    geom_text(label = c("*", "", "", "", "", "", "", ""), color = "red", size = 6, nudge_y = 30, nudge_x = 0.5) + # add starts to the significant columns
    theme_bw() +
    plot_theme
}

rt.ColuPlot
```


# Accuracy (Raw Responses)
```{r output the data for running glmm in NeSI}
path.nesi <- "NeSI"

if (TRUE) {
    fn.df <- "P101_104_106_clean"
    # write_csv(df.clean, file.path(path.nesi, paste0(fn.df, ".csv")))
    save(df.clean, file = file.path(path.nesi, paste0(fn.df, ".RData")))
}

```

## Logit Mixed Model for Accuracy

### Logit Mixed Model for the CFS condition
```{r logit mixed model -- cfs}
# build the full model (run in NeSI)
# glmm.cfs <- glmer(isCorrect ~ Congruency * Alignment +
#                      (1 + Congruency * Alignment | Participant) +
#                      (1 + Congruency * Alignment | Stimuli),
#                    data = filter(df.clean, Experiment == "CFS"),
#                    family = "binomial",
#                    verbose = TRUE,
#                    control=glmerControl(optCtrl=list(maxfun=1e6))
#                    )

load(file.path(path.nesi, "P101_glmm_cfs.RData"))

print(summary(glmm.cfs), corr=FALSE)

```


### Logit Mixed Model for the monocular condition
```{r logit mixed model -- monocular}
# build the full model (run in NeSI)
# glmm.mono <- glmer(isCorrect ~ Congruency * Alignment +
#                      (1 + Congruency * Alignment | Participant) +
#                      (1 + Congruency * Alignment | Stimuli),
#                    data = filter(df.clean, Experiment == "monocular"),
#                    family = "binomial",
#                    verbose = TRUE,
#                    control=glmerControl(optCtrl=list(maxfun=1e6))
#                    )

load(file.path(path.nesi, "P101_glmm_mono.RData"))

print(summary(glmm.mono), corr=FALSE)

```

# Versions of Packages Used
```{r versions}
sessionInfo()
```

